Paper 1 Analysis

### 2016-06-12 Articles/Article_EcolEcon_2015/Paper1/Paper1-lambda-alpha.Rnw
New graph for delta_1 distribution.

>>>>

<<rho_1-reample-dist-graph>>=
fancy_scientific <- function(l) {
     # turn in to character string in scientific notation
     l <- format(l, scientific = TRUE)
     # quote the part before the exponent to keep all the digits
     l <- gsub("^(.*)e", "'\\1'e", l)
     # turn the 'e+' into plotmath format
     l <- gsub("e", "%*%10^", l)
     # return this as an expression
     parse(text=l)
}

Rho_1_PT_data <- resampleCoeffsCES %>% 
  filter(Country == "PT") %>%
  mutate(
    delta_1_plot = 1 - delta_1
  )

ggplot(mapping = aes_string(x = "delta_1_plot")) +
  geom_density(data = Rho_1_PT_data %>% filter(method != "orig")) +
  geom_point(data = Rho_1_PT_data %>% filter(method == "orig"), aes(y = 0), shape = 4, size = 6) +
  scale_x_log10(limits = c(1e-20, 1), breaks = c(1e-20, 1e-15, 1e-10, 1e-5, 1), labels=fancy_scientific) +
  xlab(expression("1 - "*delta[1])) +
  xy_theme()
@
